% ---------- Projects Section ----------
\section*{Projects}

\Project{\href{https://ssl-manager.vercel.app/}{Multi-Tenant SSL Certificate Platform}}{
  \begin{BulletList}
    \B Designed and built a multi-tenant SSL certificate management platform using Next.js and AWS Cloud Development Kit (CDK), automating ACME-based certificate issuance and renewal across multiple DNS providers.
    \B Implemented secure, tenant-isolated infrastructure with AWS Cognito, DynamoDB, Key Management Service (KMS) encryption, Identity and Access Management (IAM) role scoping, and encrypted Amazon Simple Storage Service (S3) certificate storage.
    \B Delivered a production UI for managing domains, monitoring certificate status, and downloading standard certificate artifacts, with CI/CD-driven infrastructure and application deployments.
  \end{BulletList}
}

\Project{\href{https://tadjh.com}{Personal Portfolio Website}}{
  \begin{BulletList}
    \B Designed and built a high-performance personal portfolio using Astro, React, TypeScript, Tailwind Cascading Style Sheets (CSS), and Markdown, showcasing selected software and media projects.
    \B Implemented rich in-browser multimedia experiences, including responsive images, video, and interactive 3D content, with extensive animation and dark-mode support, while achieving a 100 Lighthouse score through performance-focused architecture and asset optimization.
    \B Automated CI/CD with GitHub Actions and Netlify for reliable, versioned deployments.
  \end{BulletList}
}

\Project{\href{https://tadjh.com/p/curtis}{Curtis Mayfield Website Redesign}}{
  \begin{BulletList}
    \B Rebuilt the Curtis Mayfield Estate website from the ground up using Next.js, replacing a static site with a component-driven architecture.
    \B Designed and implemented a custom Sanity Content Management System, enabling non-technical content updates and long-term maintainability.
    \B Delivered a dynamic, high-performance User Interface (UI) using Tailwind CSS and Framer Motion, balancing rich animation with responsiveness and performance.
  \end{BulletList}
}