% ---------- Skills Section ----------
\section*{Skills}

\Skill{Technical}{Senior-level Software and Audio Engineer with 10 years of experience building production software with TypeScript, React, and Next.js, alongside deep cloud expertise across Amazon Web Services (AWS) and Google Cloud Platform (GCP) (Infrastructure as Code (IaC), serverless, auth, data, Continuous Integration/Continuous Deployment (CI/CD), Domain Name System (DNS), and Secure Sockets Layer (SSL)). Brings 15 years of professional Pro Tools experience, combining software engineering discipline with real-world audio and media production systems.}

\Skill{Self-Motivated}{Self-directed builder who independently learns and applies new technologies, defines structure in ambiguous problems, and ships incrementally with long-term maintainability in mind. Proven through multi-year self-initiated work, including sustained freelance practice, production tools, and internally used platforms.}

\Skill{Problem Solver}{Reliability-focused problem solver who isolates root causes, makes clear architectural tradeoffs, and refactors systems for long-term stability. Emphasizes guardrails, observability, and automation to prevent recurring failures rather than treating symptoms.}

\Skill{Strong Work Ethic}{Brings disciplined and focused effort to harden systems and reach durable outcomes. Balances speed with thoroughness and continues shipping and maintaining projects even without external pressure.}

\Skill{Organized}{Maintains clear, well-structured systems through consistent naming, strong boundaries, and documentation, using organization to reduce miscommunication, speed onboarding, and keep codebases maintainable as they scale.}
